ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-07-20 pyked.tex
Add text about database, repo locations, and docs

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for unit testing, and
Travis-CI\footnote{\url{https://travis-ci.org/}} provides continuous integration
testing (i.e., runs the test suite after any new changes are made or pull-requested).

\pk{} is licensed under the permissive, open-source BSD 3-clause license. The
source code is publicly available on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}~\autocite{PyKED}. Installation of stable versions
can be accomplished from a package repository, using either \pybox|pip| to install
from \href{https://pypi.python.org/pypi}{PyPI} (Python Package Index), or
\pybox|conda| to install from the
\href{https://anaconda.org/conda-forge}{\texttt{conda-forge}} channel. In
addition, \pk{} can be installed from the source code by running
\pybox|python setup.py install| or \pybox|pip install .| from the root
directory of the repository.

@@

\ck{} and \pk{} are currently under active development, and contributions from
the community are welcomed. All development occurs under the BSD 3-clause
license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
roadmap.\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}
The highest priority issues are currently adding support for other types of
fundamental experiments, including speciation in shock tubes, flame speeds,
and flame extinction measurements. We also welcome proposals for new experimental
types; see Issue \#60 in the \pk{} repository for an example of how this may be
done.\footnote{\url{https://github.com/pr-omethe-us/PyKED/issues/60}}

>>>>

ChemKED files are stored online in a git repository hosted on GitHub.
\footnote{\url{https://github.com/pr-omethe-us/ChemKED-database}}
Submissions from the community are welcomed and can be made via the standard Pull Request
on GitHub. The authors also encourage questions and problems to be submitted either via
email or as Issues on GitHub. In particular, researchers interested in converters for
internal data formats to the ChemKED format are encouraged to reach out. In addition,
converters to and from the ReSpecTh format are available in the PyKED repository.

@@

\pk{}~\autocite{PyKED} relies on well-established scientific Python software tools.
These include NumPy~\autocite{vanderWalt:2011np} and Pandas~\autocite{pandas,McKinney2010}
for array manipulation, Pint~\autocite{Grecco2016} for interpreting and converting
between units, PyYAML~\autocite{pyyaml} for parsing YAML
files, and Cerberus for validating \ck{} files~\autocite{cerberus}.
Furthermore, \pk{} includes extensive unit, integration, and functional tests
that ensure all aspects of the software operate as intended; others have pointed
out the importance of automated testing in scientific software~\autocite{Wilson:bestpractices}.
\pk{} relies on pytest~\autocite{pytest:3.0.1} for unit testing, and currently has
100\% line and branch coverage for all of the executable code in the repository. This
means that the tests execute every line of code at least once, and every branch statement
(e.g., if-then-else statement) is tested so that every condition is executed at least
once.

Travis-CI\footnote{\url{https://travis-ci.org/pr-omethe-us/PyKED}} provides continuous
integration service, including running the test suite, building and distributing binary
installer packages, and building and publishing the online documentation. This automation
ensures that the test suite is run after every change to the source code, the
documentation is up-to-date with the latest changes, and releasing new versions is as
streamlined as possible.

\pk{} is licensed under the permissive, open-source BSD 3-clause license. The
source code is publicly available on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}~\autocite{PyKED}. Installation instructions
are available in the online documentation at
\url{https://pr-omethe-us.github.io/PyKED/install.html} and can be done via binary
packages or from the source code.

@@

\ck{} and \pk{} are currently under active development, and contributions from
the community are welcomed. All development occurs under the BSD 3-clause open source
license and the code is housed on GitHub at
\url{https://github.com/pr-omethe-us/PyKED}. Future directions for development
are outlined in the public
roadmap.\footnote{\url{https://github.com/pr-omethe-us/PyKED/wiki/Roadmap}}
The highest priority issues are currently adding support for other types of
fundamental experiments, including speciation in shock tubes, flame speeds,
and flame extinction measurements.
Questions, comments, or suggestions are welcomed and can be posted as Issues in the
GitHub repository or emailed to the authors. In particular, we welcome proposals for new
experimental types; see Issue \#60 in the \pk{} repository for an example of how this may
be done.\footnote{\url{https://github.com/pr-omethe-us/PyKED/issues/60}}
